---
title: "SamnSero Annotation Report"
date: "`r date()`"
output: 
  html_document:
    theme: cosmo
---

```{r setup, include=FALSE}
# global opts
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

```{r load-pkgs}
library(scales)
library(jsonlite)
library(htmltools)
library(fontawesome)
library(plotly)
library(ggplot2)
library(reactable)
library(crosstalk)
library(dplyr)
library(purrr)
library(stringr)
library(tidyr)
library(tibble)
library(data.table)
library(magrittr)

source("src/heatmap_plot.R")
source("src/reactable-helper.R")
```

```{r args}
# set test = 1 if running interactively
test=1

if (test != 0) {
	args <- c(getwd(),
						"../data/samnsero/sistr_res_aggregate.csv",
						"../data/samnsero/annotations/")
	src_dir <- dirname(knitr::current_input(dir = T))
} else {
	args <- commandArgs(trailingOnly = T)
	src_dir <- dirname(knitr::current_input(dir = T))
}

```

```{r main}
source(file.path(src_dir, "modules/annot/parse_args.R"))
source(file.path(src_dir, "workflow/annot_report_workflow.R"))
```

## {.tabset}

### Antimicrobial Resistance

```{r amr-html}
bscols(
	tagList(
		muiDependency(),
		amr_tbl),
	tagList(
				tags$button(tagList(fontawesome::fa("download"), "Download as CSV"),
  						onclick = "Reactable.downloadDataCSV('amr-table', 'SamnSero_AMR_annot.csv')"),
				tags$button(tagList(fontawesome::fa("filter"), "Clear Filters"),
										onclick = "Reactable.setAllFilters('amr-table', [])"),
				tags$button(tagList(fontawesome::fa("plus-circle"), "Expand/Collapse All"),
      							onclick = "Reactable.toggleAllRowsExpanded('amr-front')")),
	widths = c(12, 6)
)
```

<br>

#### {.tabset}
##### Feature Matrix

<font size="4"> 
`r fa("bell")`  **Note**: *Only genetic elements with variable presence are shown.*
</font> 

```{r amr-heatmap,fig.width=12, fig.height=12, fig.align = 'right'}
if (nrow(amr_summary != 0)) {
	plot_type(amr_summary, sistr_res_clean)
} else {
	print("Heatmap was not plotted either because only a single sample was analyzed or no variable presence elements were found")
}
```

##### Drug Class Matrix
```{r amr-drug-heatmap, fig.width =12, fig.height = 10, fig.align = 'right'}
if (nrow(amr_summary != 0)) {
	plot_class(amr_drug_summary, sistr_res_clean)
} else {
	print("Heatmap was not plotted either because only a single sample was analyzed or no variable presence elements were found")
}
```

### Virulence Factor

```{r vf-html}
bscols(
	tagList(
		muiDependency(),
		vf_tbl),
	tagList(
				tags$button(tagList(fontawesome::fa("download"), "Download as CSV"),
  						onclick = "Reactable.downloadDataCSV('vf-table', 'SamnSero_VF_annot.csv')"),
				tags$button(tagList(fontawesome::fa("filter"), "Clear Filters"),
										onclick = "Reactable.setAllFilters('vf-table', [])"),
				tags$button(tagList(fontawesome::fa("plus-circle"), "Expand/Collapse All"),
      							onclick = "Reactable.toggleAllRowsExpanded('vf-front')")),
	widths = c(12, 6)
)
```

<br>

#### {.tabset}
##### Feature Matrix

<font size="4"> 
`r fa("bell")`  **Note**: *Only genetic elements with variable presence are shown.*
</font> 

```{r vf-heatmap,fig.width=12, fig.height=12, fig.align = 'center'}
if (nrow(vf_summary != 0)) {
	plot_type(vf_summary, sistr_res_clean)
} else {
	print("Heatmap was not plotted either because only a single sample was analyzed or no variable presence elements were found")
}
```

### Plasmid

```{r plasmid-html}
bscols(
	tagList(
		muiDependency(),
		plasmid_tbl),
	tagList(
				tags$button(tagList(fontawesome::fa("download"), "Download as CSV"),
  						onclick = "Reactable.downloadDataCSV('plasmid-table', 'SamnSero_Plasmid_annot.csv')"),
				tags$button(tagList(fontawesome::fa("filter"), "Clear Filters"),
										onclick = "Reactable.setAllFilters('plasmid-table', [])")),
	widths = c(12, 6)
)
```

<br>

#### {.tabset}
##### Feature Matrix

<font size="4"> 
`r fa("bell")`  **Note**: *Only genetic elements with variable presence are shown.*
</font> 

```{r plasmid-heatmap,fig.width=12, fig.height=12, fig.align = 'center'}
if (nrow(plasmid_summary != 0)) {
	plot_type(plasmid_summary, sistr_res_clean)
} else {
	print("Heatmap was not plotted either because only a single sample was analyzed or no variable presence elements were found")
}
```

### Combined Matrix

<font size="4"> 
`r fa("bell")`  **Note**: *Only genetic elements with variable presence are shown.*
</font> 

```{r plot-full-heatmap, fig.width=15, fig.height=15, fig.align = 'center'}
if (nrow(tidy_res != 0)) {
	plot_full(tidy_res, sistr_res_clean)
} else {
	print("Heatmap was not plotted either because only a single sample was analyzed or no variable presence elements were found")
}
```

## {-}

```{js}
// JavaScript code for the Material UI range filter. This is a js language
// chunk, but you could also inline this in R using `tags$script(HTML("..."))`

const muiRangeFilter = (column, state) => {
  // Get min and max values from raw table data and memoize so it doesn't
  // have to be recalculated each time
  const range = React.useMemo(() => {
    let min = Infinity
    let max = -Infinity
    state.data.forEach(row => {
      const value = row[column.id]
      if (value < min) {
        min = Math.floor(value)
      } else if (value > max) {
        max = Math.ceil(value)
      }
    })
    return [min, max]
  }, [state.data])

  const value = column.filterValue ? column.filterValue : range
  const valueLabel = `[${value[0]}, ${value[1]}]`

  return React.createElement(
    'div',
    // Add some margin so the tooltips don't get cut off
    { style: { margin: '0 8px' } },
    [
      valueLabel,
      React.createElement(
        MaterialUI.Slider,
        {
          value: value,
          min: range[0],
          max: range[1],
          step: 0.1,
          valueLabelDisplay: 'auto',
          onChange: (e, val) => column.setFilter(val),
          'aria-label': `Filter ${column.name}`
        }
      )
    ]
  )
}

const filterRange = (rows, columnId, filterValue) => {
  const [min, max] = filterValue
  return rows.filter(row => {
    const value = row.values[columnId]
    return value >= min && value <= max
  })
}
```

```{css}
.main-container {
	max-width: 1200px
}
```

