---
title: "SamnSero Annotation Report"
date: "`r date()`"
output: 
  html_document:
    theme: cosmo
---

```{r setup, include=FALSE}
# global opts
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

```{r load-pkgs}
library(scales)
library(jsonlite)
library(htmltools)
library(fontawesome)
library(plotly)
library(ggplot2)
library(reactable)
library(crosstalk)
library(dplyr)
library(purrr)
library(stringr)
library(tidyr)
library(tibble)
library(data.table)
library(magrittr)
```

```{r args}
# set interactive to 1 if running interactively
interactive = 0

# get where the .Rmd file is
src_dir <- dirname(knitr::current_input(dir = T))

# get positional arguments
if (interactive == 1) {
	args <- c("../data/samnsero_annot_081222/sistr_res_aggregate.csv",
						"../data/samnsero_annot_081222/annotations/")
} else {
	args <- commandArgs(trailingOnly = T)
}

# set p_dim default values
p_dim <- c(1,1)
```

```{r main}
source(file.path(src_dir, "src/heatmap_plot.R"))
source(file.path(src_dir, "src/reactable-helper.R"))
source(file.path(src_dir, "modules/annot/parse_args.R"))
source(file.path(src_dir, "workflow/annot_report_workflow.R"))
```

<style>
  .container {
    overflow: scroll !important;
    white-space: nowrap;
    max-width: 1200px;
    max-height: 1000px;
  }
  img {
    max-width: 1000%;
  }
</style>

# {.tabset}

## Antimicrobial Resistance

```{r amr-html}
if (exists("amr_tbl")) {
	
	bscols(
		tagList(
			muiDependency(),
			amr_tbl),
		tagList(
					tags$button(tagList(fontawesome::fa("download"), "Download as CSV"),
	  						onclick = "Reactable.downloadDataCSV('amr-table', 'SamnSero_AMR_annot.csv')"),
					tags$button(tagList(fontawesome::fa("filter"), "Clear Filters"),
											onclick = "Reactable.setAllFilters('amr-table', [])"),
					tags$button(tagList(fontawesome::fa("circle-plus"), "Expand/Collapse All"),
	      							onclick = "Reactable.toggleAllRowsExpanded('amr-front')")),
		widths = c(12, 6)
	)
	
}
```

<br>

### {.tabset}
#### Feature Matrix

##### {.tabset .tabset-pills}
###### Variable only

<br>

<font size="4"> 
`r fa("bell")`  **Note**: *Only genetic elements with variable presence are shown.*
</font> 

```{r amr-heatmap-var}
if (tryCatch(nrow(amr_summary_var) == 0 | ncol(amr_summary_var) <= 1, error = function(e) return(T))) {
	
	print("Heatmap was not plotted either because only a single sample was analyzed or no variable presence elements were found")
	heatmap_eval = F
	
} else {
	
	#p <- plotly_type(amr_summary_var, sistr_res_clean)
	#p_dim <- calc_ht_size(p)
	p_dim <- c(ncol(amr_summary_var)*0.9+2, nrow(amr_summary_var)*0.25+2)
	heatmap_eval = T
	
}
```

<div class="container">
```{r amr-heatmap-var-plot, eval=heatmap_eval, fig.width = p_dim[1], fig.height = p_dim[2], fig.align = 'right'}
#draw(p, heatmap_legend_side = "top",annotation_legend_side = "left")
plotly_type(amr_summary_var, sistr_res_clean)
```
</div>

###### Variable + Invariable

<br>

<br>

```{r amr-heatmap}
if (tryCatch(nrow(amr_summary) == 0 | ncol(amr_summary) <= 1, error = function(e) return(T))) {
	
	print("Heatmap was not plotted either because only a single sample was analyzed or no elements were found")
	heatmap_eval = F
	
} else {
	
	#p <- plotly_type(amr_summary, sistr_res_clean)
	#p_dim <- calc_ht_size(p)
	p_dim <- c(ncol(amr_summary)*0.9+2, nrow(amr_summary)*0.25+2)
	heatmap_eval = T
	
}
```

<div class="container">
```{r amr-heatmap-plot,  fig.width = p_dim[1], fig.height = p_dim[2], fig.align = 'right', eval = heatmap_eval}
#draw(p, heatmap_legend_side = "top",annotation_legend_side = "left")
plotly_type(amr_summary, sistr_res_clean)
```
</div>

##### {-}

#### Drug Class Matrix

<br>

<br>

<div class="container">
```{r amr-drug-heatmap}
if (tryCatch(nrow(amr_drug_summary) == 0 | ncol(amr_drug_summary) <= 1, error = function(e) return(T))) {
	
	print("Heatmap was not plotted either because only a single sample was analyzed or no elements were found")
	heatmap_eval = F
	
} else {
	
	#p <- plot_class(amr_drug_summary, sistr_res_clean)
	#p_dim <- calc_ht_size(p)
	p_dim <- c(ncol(amr_drug_summary)*0.9+2, nrow(amr_drug_summary)*0.25+2)
	heatmap_eval = T
	
}
```

```{r amr-drug-heatmap-plot, fig.width = p_dim[1], fig.height = p_dim[2], fig.align = 'center', eval=heatmap_eval}
#draw(p, heatmap_legend_side = "top", annotation_legend_side = "left")
plotly_class(amr_drug_summary, sistr_res_clean)
```
</div>

## Virulence Factor

```{r vf-html}
if (exists("vf_tbl")) {
	
	bscols(
		tagList(
			muiDependency(),
			vf_tbl),
		tagList(
					tags$button(tagList(fontawesome::fa("download"), "Download as CSV"),
	  						onclick = "Reactable.downloadDataCSV('vf-table', 'SamnSero_VF_annot.csv')"),
					tags$button(tagList(fontawesome::fa("filter"), "Clear Filters"),
											onclick = "Reactable.setAllFilters('vf-table', [])"),
					tags$button(tagList(fontawesome::fa("circle-plus"), "Expand/Collapse All"),
	      							onclick = "Reactable.toggleAllRowsExpanded('vf-front')")),
		widths = c(12, 6)
	)
	
}
```

<br>

### {.tabset}
#### Feature Matrix

##### {.tabset .tabset-pills}
###### Variable only

<br>

<font size="4"> 
`r fa("bell")`  **Note**: *Only genetic elements with variable presence are shown.*
</font> 

<div class="container">
```{r vf-heatmap-var}
if (tryCatch(nrow(vf_summary_var) == 0 | ncol(vf_summary_var) <= 1, error = function(e) return(T))) {
	
	print("Heatmap was not plotted either because only a single sample was analyzed or no variable presence elements were found")
	heatmap_eval = F
	
} else {
	
	#p <- plot_type(vf_summary_var, sistr_res_clean)
	p_dim <- c(ncol(vf_summary_var)*0.9+2, nrow(vf_summary_var)*0.25+2)
	heatmap_eval = T
	
}
```

```{r vf-heatmap-var-plot, fig.width = p_dim[1], fig.height = p_dim[2], fig.align = 'center', eval=heatmap_eval}
#draw(p, heatmap_legend_side = "top", annotation_legend_side = "left")
plotly_type(vf_summary_var, sistr_res_clean)
```
</div>

###### Variable + Invariable

<br>

<br>

<div class="container">
```{r vf-heatmap}
if (tryCatch(nrow(vf_summary) == 0 | ncol(vf_summary) <= 1, error = function(e) return(T))) {
	
	print("Heatmap was not plotted either because only a single sample was analyzed or no elements were found")
	heatmap_eval = F
	
} else {
	
	#p <- plot_type(vf_summary, sistr_res_clean)
	#p_dim <- calc_ht_size(p)
	p_dim <- c(ncol(vf_summary)*0.9+2, nrow(vf_summary)*0.25+2)
	heatmap_eval = T
	
}
```

```{r vf-heatmap-plot, fig.width = p_dim[1], fig.height = p_dim[2], fig.align = 'center', eval=heatmap_eval}
#draw(p, heatmap_legend_side = "top", annotation_legend_side = "left")
plotly_type(vf_summary, sistr_res_clean)
```
</div>


## Plasmid

```{r plasmid-html}
if (exists("plasmid_tbl")) {
	
	bscols(
		tagList(
			muiDependency(),
			plasmid_tbl),
		tagList(
					tags$button(tagList(fontawesome::fa("download"), "Download as CSV"),
	  						onclick = "Reactable.downloadDataCSV('plasmid-table', 'SamnSero_Plasmid_annot.csv')"),
					tags$button(tagList(fontawesome::fa("filter"), "Clear Filters"),
											onclick = "Reactable.setAllFilters('plasmid-table', [])")),
		widths = c(12, 6)
	)

}
```

<br>

### {.tabset}
#### Feature Matrix

##### {.tabset .tabset-pills}
###### Variable only

<br>

<font size="4"> 
`r fa("bell")`  **Note**: *Only genetic elements with variable presence are shown.*
</font> 

<div class="container">
```{r plasmid-heatmap-var}
if (tryCatch(nrow(plasmid_summary_var) == 0 | ncol(plasmid_summary_var) <= 1, error = function(e) return(T))) {
	
	print("Heatmap was not plotted either because only a single sample was analyzed or no variable presence elements were found")
	heatmap_eval = F
	
} else {
	
	#p <- plot_type(plasmid_summary_var, sistr_res_clean)
	#p_dim <- calc_ht_size(p)
	p_dim <- c(ncol(plasmid_summary_var)*0.9+2, nrow(plasmid_summary_var)*0.25+2)
	heatmap_eval = T
	
}
```

```{r plasmid-heatmap-var-plot, fig.width=p_dim[1], fig.height=p_dim[2]+1, fig.align = 'center', eval=heatmap_eval}
#draw(p, heatmap_legend_side = "top", annotation_legend_side = "left")
plotly_type(plasmid_summary_var, sistr_res_clean)
```
</div>

###### Variable + Invariable

<br>

<br>

<div class="container">
```{r plasmid-heatmap}
if (tryCatch(nrow(plasmid_summary) == 0 | ncol(plasmid_summary) <= 1, error = function(e) return(T))) {
	
	print("Heatmap was not plotted either because only a single sample was analyzed or no elements were found")
	heatmap_eval = F
	
} else {
	
	#p <- plot_type(plasmid_summary, sistr_res_clean)
	#p_dim <- calc_ht_size(p)
	p_dim <- c(ncol(plasmid_summary)*0.9+2, nrow(plasmid_summary)*0.25+2)
	heatmap_eval = T
	
}
```

```{r plasmid-heatmap-plot, fig.width=p_dim[1], fig.height=p_dim[2]+1, fig.align = 'center', eval=heatmap_eval}
#draw(p, heatmap_legend_side = "top", annotation_legend_side = "left")
plotly_type(plasmid_summary, sistr_res_clean)
```
</div>


## Combined Matrix

### {.tabset .tabset-pills}

#### Variable only

<br>

<font size="4"> 
`r fa("bell")`  **Note**: *Only genetic elements with variable presence are shown.*
</font> 

<div class="container">
```{r full-heatmap-var}
if (tryCatch(ncol(tidy_res_var) <= 1 | nrow(tidy_res_var) == 0, error = function(e) return(T))) {
	
	print("Heatmap was not plotted either because only a single sample was analyzed or no variable presence elements were found")
	heatmap_eval = F
	
} else {
	
	p <- plot_full(tidy_res_var, sistr_res_clean)
	p_dim <- calc_ht_size(p)
	heatmap_eval = T
	
}
```

```{r plot-full-heatmap-var, fig.width=p_dim[1], fig.height=p_dim[2]+1, fig.align = 'center', eval=heatmap_eval}
draw(p, heatmap_legend_side = "top", annotation_legend_side = "left")
```
</div>

#### Variable + Invariable

<br>

<br>

<div class="container">
```{r full-heatmap}
if (tryCatch(ncol(tidy_res) <= 1 | nrow(tidy_res) == 0, error = function(e) return(T))) {
	
	print("Heatmap was not plotted either because only a single sample was analyzed or no elements were found")
	heatmap_eval = F
	
} else {
	
	p <- plot_full(tidy_res, sistr_res_clean)
	p_dim <- calc_ht_size(p)
	heatmap_eval = T
	
}
```

```{r plot-full-heatmap, fig.width=p_dim[1], fig.height=p_dim[2]+1, fig.align = 'center', eval=heatmap_eval}
draw(p, heatmap_legend_side = "top", annotation_legend_side = "left")
```
</div>

# {-}

```{js}
// JavaScript code for the Material UI range filter. This is a js language
// chunk, but you could also inline this in R using `tags$script(HTML("..."))`

const muiRangeFilter = (column, state) => {
  // Get min and max values from raw table data and memoize so it doesn't
  // have to be recalculated each time
  const range = React.useMemo(() => {
    let min = Infinity
    let max = -Infinity
    state.data.forEach(row => {
      const value = row[column.id]
      if (value < min) {
        min = Math.floor(value)
      } else if (value > max) {
        max = Math.ceil(value)
      }
    })
    return [min, max]
  }, [state.data])

  const value = column.filterValue ? column.filterValue : range
  const valueLabel = `[${value[0]}, ${value[1]}]`

  return React.createElement(
    'div',
    // Add some margin so the tooltips don't get cut off
    { style: { margin: '0 8px' } },
    [
      valueLabel,
      React.createElement(
        MaterialUI.Slider,
        {
          value: value,
          min: range[0],
          max: range[1],
          step: 0.1,
          valueLabelDisplay: 'auto',
          onChange: (e, val) => column.setFilter(val),
          'aria-label': `Filter ${column.name}`
        }
      )
    ]
  )
}

const filterRange = (rows, columnId, filterValue) => {
  const [min, max] = filterValue
  return rows.filter(row => {
    const value = row.values[columnId]
    return value >= min && value <= max
  })
}
```

```{css}
.main-container {
	max-width: 1200px
}
```

